--
title: "Homework: Use R as GIS"
output: github_document
---
Based on the accident dataset ('accident.dbf') we used last week, please
write R scripts to finish the following two tasks:

1. Map the locations of accidents based on the lat/long and use the United
   States state boundary as the background (the boundary shapefile is in
   the folder 'Data/US'). The result map should have the basic cartographic
   elements (e.g., map scale, compass). Please note the `accident.dbf` can
   be loaded by the following codes, and there are invalid values for
   lat/long column that you probably need to clean up before use (see the
   example code in the homework \#2).  

```{r load, eva=T, echo=T, results='hide'}
library(foreign)
accident=read.dbf('Data/accident.dbf')

# Step 1: Clean up the data first

# Step 2: Map 

```

2. In the folder 'Data/Texas' contains the boundary of Texas counties.
   Using the `accident.dbf' data, please count the number of accidents for
   each county and make a county map based on the value of count you
   calculated. 

```{r texas, eva=T, echo=T, results='hide'}
library(foreign)
accident=read.dbf('Data/accident.dbf')

# Use the function  *over()*; see the example codes for the case of bears and parks
# in the lecture

```

